Panel Seminars

### 2023-03-20 ADMIN_01_submissions_instructions.Rmd
implementing new organizational structure to repo

---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: "RCN_site-Nov05.bib"
editor_options: 
  markdown: 
    wrap: 72
---

@@

-   add your citations to the RCN_site-Nov05.bib document by exporting
    BibTeX-formatted citations from your reference manager
-   add the line 'bibliography: RCN_site-Nov05.bib' to your header at
    the top of the .Rmd document, which looks like this:

@@

    ---
    title: "Instructions for developing new pages for the MarineOmics webpage"
    bibliography: RCN_site-Nov05.bib
    ---

@@

    knitr::include_graphics("Rivera_etal_fig.png")

>>>>

---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: "ADMIN_01_submissions_instructions_files/common-bib_01.bib"
editor_options: 
  markdown: 
    wrap: 72
---

@@

-   add your citations to the common-bib_01.bib document by exporting
    BibTeX-formatted citations from your reference manager
-   add the line 'bibliography: common-bib_01.bib' to your header at
    the top of the .Rmd document, which looks like this:

@@

    ---
    title: "Instructions for developing new pages for the MarineOmics webpage"
    bibliography: common-bib_01.bib
    ---

@@

    knitr::include_graphics("ADMIN_01_submissions_instructions_files/Rivera_etal_fig.png")

### 2023-03-20 ADMIN_02_contributions.Rmd
implementing new organizational structure to repo

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# How to contribute new material to the MarineOmics.github.io website
If you are interested in submitting new content to the
MarineOmics.github.io website, we have a [guide](submissions_instructions.html) for you!
While the website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content. The guide provides general instructions as well as examples of how to build specific features (eg., tables, code chunks). Prior to developing new pages, please contact the current Website Manager Jason Johns (jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other questions, comments, or features you'd like added to the guide.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# How to contribute new material to the MarineOmics.github.io website
If you are interested in submitting new content to the
MarineOmics.github.io website, we have a [guide](ADMIN_01_submissions_instructions.html) for you!
While the website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content. The guide provides general instructions as well as examples of how to build specific features (eg., tables, code chunks). Prior to developing new pages, please contact the current Website Manager Jason Johns (jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other questions, comments, or features you'd like added to the guide.

### 2023-03-20 FUN_01_DGE_comparison_v2.Rmd
implementing new organizational structure to repo

---
title: "Fitting Multifactorial Models of Differential Expression"
subtitle: '*Samuel N. Bogan*'
bibliography: DGE_Comp.bib
---

@@

# Read in matrix of RSEM expected read counts
data <- read.delim("RNA_data/GE2_expected_counts_gene.matrix", sep = "\t", header = T, row.names = 1)

@@

knitr::include_graphics("images/Rivera_etal_fig.png")

>>>>

---
title: "Fitting Multifactorial Models of Differential Expression"
subtitle: '*Samuel N. Bogan*'
bibliography: FUN_01_DGE_comparison_v2_files/DGE_Comp.bib
---

@@

# Read in matrix of RSEM expected read counts
data <- read.delim("FUN_01_DGE_comparison_v2_files/RNA_data/GE2_expected_counts_gene.matrix", sep = "\t", header = T, row.names = 1)

@@

knitr::include_graphics("FUN_01_DGE_comparison_v2_files/Rivera_etal_fig.png")

### 2023-03-20 POP_01_choosing_population_genetics.Rmd
implementing new organizational structure to repo

---
bibliography: RCN_site-Nov05.bib
title: Choosing a Population Genomics Approach
---

@@

![**Figure 1** from [@Lou2021-me] comparing the distribution of sequencing reads mapped to a reference genome.](images/mec16077-fig-0001-m.jpg)

@@

# Recommended readings  
Below we list a number of great review articles and empirical comparison studies that can help when making the decision. This topic was also discussed during the [MarineOmics seminars](https://marineomics.github.io/panels.html).

@@

* [RADseq](RADseq.html)  
* [hcWGS](WGS_intro.html)
* [lcWGS, maintained by MarineOmics member Nicolas Lou](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Poolseq](poolseq.html)

>>>>

---
bibliography: POP_01_choosing_population_genetics_files/common-bib_01.bib
title: Choosing a Population Genomics Approach
---

@@

![**Figure 1** from [@Lou2021-me] comparing the distribution of sequencing reads mapped to a reference genome.](POP_01_choosing_population_genetics_files/mec16077-fig-0001-m.jpg)

@@

# Recommended readings  
Below we list a number of great review articles and empirical comparison studies that can help when making the decision. This topic was also discussed during the [MarineOmics seminars](https://marineomics.github.io/ADMIN_03_panels.html).

@@

* [RADseq](POP_02_RADseq.html)  
* [hcWGS](POP_04_WGS_intro.html)
* [lcWGS, maintained by MarineOmics member Nicolas Lou](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Poolseq](POP_03_poolseq.html)

### 2023-03-20 POP_04_WGS_intro.Rmd
implementing new organizational structure to repo

---
bibliography: RCN_site-Nov05.bib
title:  Whole Genome Resequencing for Population Genomics 
subtitle: '*Katherine Silliman, Nicolas Lou*'
---

@@

* [Fastq-to-VCF SnakeMake pipeline](fastq2vcf_june2022_update.html): in-depth explanation of an automated short-read mapping and variant calling pipeline maintained by [Harvard Informatics](https://github.com/harvardinformatics/shortRead_mapping_variantCalling). Useful if you plan to adopt this pre-packaged automated and parallelizable pipeline, and would like to understand its different components, but not necessarily change it substantially.

* [Fastq-to-VCF workflow](WGS-Full-Walkthrough.html): detailed walkthrough of processing 15x sequencing depth WGS data for cod, from raw reads to a VCF. Useful if you would like to run each component of the pipeline yourself and potentially tweak some of them for your own purpose. In other words, you can more easily add, skip, or change parts of this pipeline, but will lose the convenience offered by an automated pipeline.

>>>>

---
bibliography: POP_04_WGS_intro_files/common-bib_01.bib
title:  Whole Genome Resequencing for Population Genomics 
subtitle: '*Katherine Silliman, Nicolas Lou*'
---

@@

* [Fastq-to-VCF SnakeMake pipeline](POP_06_fastq2vcf_june2022_update/POP_06_fastq2vcf_june2022_update.html): in-depth explanation of an automated short-read mapping and variant calling pipeline maintained by [Harvard Informatics](https://github.com/harvardinformatics/shortRead_mapping_variantCalling). Useful if you plan to adopt this pre-packaged automated and parallelizable pipeline, and would like to understand its different components, but not necessarily change it substantially.

* [Fastq-to-VCF workflow](POP_07_WGS_Full_Walkthrough/POP_07_WGS_Full_Walkthrough.html): detailed walkthrough of processing 15x sequencing depth WGS data for cod, from raw reads to a VCF. Useful if you would like to run each component of the pipeline yourself and potentially tweak some of them for your own purpose. In other words, you can more easily add, skip, or change parts of this pipeline, but will lose the convenience offered by an automated pipeline.

### 2023-03-20 POP_05_RDAtraitPredictionTutorial.Rmd
implementing new organizational structure to repo

![](rda_tutorial/multivar.png)

@@

G <- read.table(unz("rda_tutorial/Genotypes.txt.zip", "Genotypes.txt"))
dim(G) # 1000 individuals and 26371 loci

ind <- read.table("rda_tutorial/Individuals.txt", header=TRUE)
dim(ind) #corresponds to rows in G
head(ind)

muts <-  read.table("rda_tutorial/SNPs.txt", header=TRUE)
dim(muts) #corresponds to columns in G
head(muts)

>>>>

![](multivar.png)

@@

G <- read.table(unz("POP_05_RDAtraitPredictionTutorial_files/Genotypes.txt.zip", "Genotypes.txt"))
dim(G) # 1000 individuals and 26371 loci

ind <- read.table("POP_05_RDAtraitPredictionTutorial_files/Individuals.txt", header=TRUE)
dim(ind) #corresponds to rows in G
head(ind)

muts <-  read.table("POP_05_RDAtraitPredictionTutorial_files/SNPs.txt", header=TRUE)
dim(muts) #corresponds to columns in G
head(muts)

### 2023-03-20 index.Rmd
implementing new organizational structure to repo

* [Choosing a population genomics sequencing approach](choosing-population-genetics.html)  
* [Whole Genome Resequencing (WGS)](WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](RADseq.html) 
* [Poolseq](poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](RDAtraitPredictionTutorial.html)

@@

* [Multifactorial RNAseq analyses](DGE_comparison_v2.html)  
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods

@@

# Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!

@@

# Making contributions to the MarineOmics.github.io website {#contributions}
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).

>>>>

* [Choosing a population genomics sequencing approach](POP_01_choosing_population_genetics.html)  
* [Whole Genome Resequencing (WGS)](POP_04_WGS_intro.html)  
  * [Low coverage WGS](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Reduced Representation Sequencing](POP_02_RADseq.html) 
* [Poolseq](POP_03_poolseq.html)
* [Redundancy Analysis (RDA) Trait Prediction](POP_05_RDAtraitPredictionTutorial.html)

@@

* [Multifactorial RNAseq analyses](FUN_01_DGE_comparison_v2.html)  
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods

@@

# Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](ADMIN_03_panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!

@@

# Making contributions to the MarineOmics.github.io website {#contributions}
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](ADMIN_01_submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
